A New Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Systems

### 2022-04-20 notes/notes.tex
proved orthonormality of eigenstates

	\Psi^n_{\vec k}\left(\left\{ \vec r_k \right\} \right) = \frac{1}{\sqrt N}\sum_{i} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i\right)
where \(N\) is the total number of lattice sites. The interpretation is that the set of \(n=0\) states form the lowest band in the spectrum of the lattice. Higher values of \(n\) produce the more energetic bands. The ground state is obtained by setting \(\vec k\) and \(n\) to 0: \(\ket{\Psi_{\vec k=0}^{n=0}} \equiv \ket{\Psi_\text{gs}}\)To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:

>>>>

	\ket{\Psi^n_{\vec k}\left(\left\{ \vec r_k \right\} \right)} = \frac{1}{\sqrt N}\sum_{\vec R_i} e^{i \vec{k}\cdot\vec{R}_i} \ket{\psi^n_\text{aux}\left(\vec R_i\right)}
where \(N\) is the total number of lattice sites. The interpretation is that the set of \(n=0\) states form the lowest band in the spectrum of the lattice. Higher values of \(n\) produce the more energetic bands. The ground state is obtained by setting \(\vec k\) and \(n\) to 0: \(\ket{\Psi_{\vec k=0}^{n=0}} \equiv \ket{\Psi_\text{gs}}\). These states form an orthonormal basis:
	&\braket{\Psi^m_{\vec k^\prime} | \Psi^n_{\vec k}} \\
	&= \frac{1}{N}\sum_{\vec R_i, \vec R_j} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}^m\left( \vec R_j \right) | \psi_\text{aux}^n\left( \vec R_i \right)} = \frac{1}{N}\sum_{\vec R_i, \vec R_j} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}^m\left( \vec R_0 \right) T^\dagger\left( \vec R_0 - \vec R_j \right) T\left( \vec R_0 - \vec R_i \right) | \psi_\text{aux}^n\left( \vec R_0 \right)}\\
	&= \frac{1}{N}\sum_{\vec R_i, \vec R_j, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}^m\left( \vec R_0 \right) T\left( \vec R_j - \vec R_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}^n\left( \vec R_0 \right)}\\
	&= \frac{1}{N}\sum_{\vec R_i, \vec R_j, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}^m\left( \vec R_0 \right) e^{i \vec q \cdot \left( \vec R_j - \vec R_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}^n\left( \vec R_0 \right)} \\
	&= N \delta_{\vec k, \vec k^\prime}\braket{\psi_\text{aux}^m\left( \vec R_0 \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}^n\left( \vec R_0 \right)}, ~ ~ ~ \left[\because \sum_{\vec R_i}e^{i \vec R_i \left( \vec k - \vec q \right) }\sum_{\vec R_j}e^{i \vec R_j \left( \vec q - \vec k^\prime \right) } = N \delta_{\vec k,\vec q}N \delta_{\vec k^\prime,\vec q} \right]\\
	&= \delta_{\vec k, \vec k^\prime}\int \prod_{\vec r_k}d\vec r_k~ \psi_\text{aux}^m\left( \left\{\vec r_k\right\} \right) e^{i \vec k \cdot \sum \vec r_k} \prod_{\vec r_k^\prime} d\vec r_k^\prime~ e^{-i \vec k \cdot \sum \vec r^\prime_k} \psi_\text{aux}^n\left( \left\{\vec r_k^\prime\right\} \right)
The local nature of the auxiliary model wavefunctions ensures that the product of two auxiliary model wavefunctions will be non-zero only in the common region: \(\psi_\text{aux}^m\left( \left\{\vec r_k\right\} \right) \psi_\text{aux}^n\left( \left\{\vec r_k^\prime\right\}\right) \simeq \delta_{\vec r_k, \vec r_k^\prime} \psi_\text{aux}^m\left( \left\{\vec r_k\right\} \right) \psi_\text{aux}^n\left( \left\{\vec r_k\right\}\right)\). Substituting this and dropping the \(\prod\) for brevity gives
	\braket{\Psi^m_{\vec k^\prime} | \Psi^n_{\vec k}} = \delta_{\vec k, \vec k^\prime}\int d\vec r_k~ d\vec r_k^\prime~ \delta_{\vec r_k, \vec r_k^\prime} \psi_\text{aux}^m\left(\left\{\vec r_k\right\}\right) \psi_\text{aux}^n\left(\left\{\vec r_k\right\}\right) e^{i \vec k \cdot \sum \left(\vec r_k - \vec r^\prime_k\right) } = \delta_{\vec k, \vec k^\prime}\int d\vec r_k \psi_\text{aux}^m\left(\left\{\vec r_k\right\}\right) \psi_\text{aux}^n\left(\left\{\vec r_k\right\}\right) = \delta_{\vec k,\vec k^\prime}\delta_{m,n}
At the last step, we used the orthonormality of the eigenstates of the auxiliary model: \(\int \prod_{\vec r_k} d\vec r_k \psi_\text{aux}^m\left(\left\{\vec r_k\right\}\right) \psi_\text{aux}^n\left(\left\{\vec r_k\right\}\right) = \delta_{m,n}\).

To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:
